---
# SECTION: Bibliography opts
# bibliography: "./refs/refs.bib"
# cite-method: citeproc
# citeproc: true
# csl: "../../resources/bibs/apa-cv.csl"
# link-citations: true
# link-bibliography: true
suppress-bibliography: true
---

```{r}
#| lst-label: lst-r-libraries
#| lst-cap: "R libraries"

base::library(package = kableExtra)
base::library(package = knitr) # NOTE: For document rendering
base::library(package = quarto) # NOTE: For document framework
knitr::write_bib(
  x    = base::.packages(),
  file = "./refs/r_packages.bib"
)
```

```{r}
#| lst-label: lst-knitr-opts
#| lst-cap: "Knitr options"

base::options(knitr.kable.NA = "-")
```

# Accessibility {#sec-accessibility}

You can obtain a digital copy of this handout on the FTLC Conference Website or
by following the QR code below.

The digital copy of this document is designed to be friendly to assistive
technologies and software. Please contact me at
[QuagliaQ@gvsu.edu](mailto:QuagliaQ@gvsu.edu) with any issues

*QR CODE HERE*

# Assumptions Surrounding Tests {#sec-assumptions}

## Agreeable Assumptions {#sec-agree-on}

*Some reasonable and straightforward factual statements about tests*

- Summative, timed, proctored, and closed-note exams are still one of the most
  **popular** ways to test knowledge in higher education
- There is a long history and **precedence** to using this format of exam
- Exams in this format are among the most **secure** way to administers to assess
  knowledge

## Debatable Assumptions {#sec-debatable}

*Some subjective statements about tests*

- Exams are more **anxiety-inducing** than other forms of assessment
- Timed exams risk being **biased** against students who process slower or those
  with test anxiety
- Exams **stifle** creative problem solving or broader approaches to solutions

## Controversial Assumptions {#sec-controversial}

*Some statements that I will give you tools to explore in your own tests*

- Traditional exams still have **value and accuracy** in gauging something about
  the knowledge of a student
- While there will always be an element of bias, an exam can be made and
  re-examined to be **reasonably fair** to all students
- When responsibly designed and planned, a test can **strengthen relationships**
  between a student and faculty member

# Before the Test {#sec-before}

## Best Practices for (Humbly) Designing Test Questions {#sec-humble}

- *Always* have a clear, specific reference/citation to where a correct answer
  is pulled from - to textbook, lecture notes, etc. Consider including this on
  the test itself
- Review questions before each test administration, even if unchanged since last
  time
-

# After the Test {#sec-after}

{{< important "In general, try to make decisions about individual items, not the
test as a whole." >}}

## Understanding Test Item Metrics {#sec-test-metrics}

**"Difficulty"**

- Each question has $P$ or the proportion of students that got a question
  correct, e.g. $P = 0.80$ means 80% of students got a question correct
- Higher $P \rightarrow$ easier question

**"Discrimination"**

- How well does a question correlate to the test as a whole? Usually given as
  $r_{pbis}$ or the point-biserial correlation, e.g. $r_{pbis} = 0.60$ means a
  high degree of correlation with the test
- Higher, positive $r_{pbis}$ greater discrimination

**"Subjective Content Relevance"**

- Was a question about a central, learning objective-related concept? Or a
  footnote?
- How many times was this concept covered, and in how many different mediums

## Responding to Test Item Metrics {#sec-responding}

- **Red flag items:** those that are both difficult ($P < 0.30$) and poorly
  discriminating ($r_{pbis} < 0.20$); examine each with subjective content
  relevance - does this question capture the student's knowledge in this domain
  well?

- **Options for responding:**
  - "Dropping" a test item: remove it from the test entirely, but hurts those
    who got it right; most conservative solution
  - "Nullifying" a test item: giving full credit to several or all possible
    choices, giving a "freebie" to all students; most generous solution
  - "Curving" the test as a whole: provides all students with a boost, but is
    primarily focused on a certain average or grade outcome; indifferent to
    actual question performance
  - Ignore it
